DIAGNOSTIC SUPPORT OF SKIN LESION CLASSIFICATION USING CNN AND SOFT ATTENTION

### 2022-08-19 MDPI/Sensor Paper/template.tex
Update

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-2566-5637} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Khoi Do Hoang$^{
		2,\dagger,%\ddagger
	}$\orcidA{}*}

@@

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Khoi Do}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Do, K.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

@@

\address{
$^{1}$ \quad Lecturer: Viet Dung Nguyen; dung.nguyenviet1@hust.edu.vn\\
$^{2}$ \quad Author: Khoi Do Hoang; khoi.dh200332@sis.hust.edu.vn}

% Contact information of the corresponding author
\corres{Correspondence: khoido8899@gmail.com; Tel.: +84-9360-192-58}

% Current address and/or shared authorship
\firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Viet Nam} 
\secondnote{}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

\section{Introduction} 
\subsection{Problem Statement}
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.

Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to build solutions to a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions to the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.

In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.

\subsection{Related Works}
Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in\cite{03358}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.

@@

Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3\cite{00567} model. In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set. Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.

Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process.

@@

Another state of the art is GradCam and Kernel SHAP\cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research they use three data sets containing HAM10000, BCN-20000 and MSK. Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass.

On the other hand, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021\cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn.

SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.

@@

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al.

\begin{table}
	\centering
	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
		\hline
		Research & Deep Learning & Machine Learning & Data 
		Augmentation & Feture Extraction & Data set\\
		\hline
		\cite{03358} & x & & x & & HAM10000\\
		\hline
		\cite{03798} & x & x & x & x & HAM10000\\
		\hline
		\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
		\hline
		\cite{09418} & x & & x & & HAM10000\\
		\hline
		\cite{01284} & x & & x & & HAM10000\\
		\hline
		\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
		\hline
		\cite{03225} & x & & x & & HAM10000\\
		\hline
		\cite{12602} & x & & x & & HAM10000\\
		\hline
		\cite{03426} & x & & x & & HAM10000\\
		\hline
		\cite{03910} & x & & x & & HAM10000\\
		\hline
		\cite{05045} & & x & x & x & HAM10000\\
		\hline
	\end{tabular}
	\caption{Related Works Summary. This table is a summary of the approach to skin lesion classification and segmentation. The first column illustrate the cite to the paper research. Column 2 shows a brief summary of the method that is stated in the associated paper.}
	\label{table:related-work-summary}
\end{table}
\subsection{Proposed Method}
In this research, a new model is constructed from the combination of:\\
- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
- Using metadata including age, gender, localization as another input of the model\\
- Using Soft-Attention as a feature extractor of the model\\
- A new weight loss function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Materials}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse\cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the table below:

@@

\subsubsection{Metadata}
The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position 
\begin{table}[H]
	\centering
	\begin{tabular}{|c c c c |} 
		\hline
		ID & Age & Gender & Local\\ 
		\hline
		ISIC-00001 & 15 & Male & back\\
		\hline
		ISIC-00002 & 85 & Female & elbow\\
		\hline
	\end{tabular}
	\caption{Metadata example in the data set}
	\label{table:metadata sample}
\end{table}
\subsection{Methodology}
\subsubsection{Overall Architecture}
The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer. It is described in the figure below:

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/MainModel - Model Form}
	\caption{Overall Model Architecture}
	\label{fig:main-model}
\end{figure}

The figure 6 illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research. In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module. Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module. InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module. Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module. 
\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/Model Structure}
	\caption{Overall Model Architecture. This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge. The detail structure and information can be found at the Apendix A}
	\label{fig:model-structure}
\end{figure}
The figure 7, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module. The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell. 
\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
	\caption{Overall Mobile-based Model Architecture. This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detail structure and information can be found at the Apendix B}
	\label{fig:mobile-model-structure}
\end{figure}

\subsubsection{Input Schema}
In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form. Before feeding into the backbone model, the images is pre-processed by the input requirement of each model. DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.

On the other hand, the metadata is also used as another input. In paper\cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU\cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

In this paper, the unknowns is kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section. The Input schema is described as follow:

@@

\subsubsection{Backbone Model}
In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.

\begin{table}[H]
	\centering
	\begin{tabular}{|l | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2\cite{07261} & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
	\caption{Size and Parameters and Depth of backbone model used in this paper. This table summarizes the properties of the backbone models. The size column illustrates how many space need to store the model in megabyte. The parameters column demonstrate the number of parameters in the associated model. The last column, depth show the number of hidden layers in that model. Parameters and Depth are two crucial element to evaluate the optimized model stated in the Objective section.}
	\label{table:model-summary}
\end{table}

\subsubsection{Soft-Attention}
Applying the Soft-Attention layer in deep learning is not a new approach. Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describes the flow of the Soft-Attention module:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the softmax function to generate K (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

@@

In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:

@@

After feeding into ReLU function layer, the feature map is processed in two paths. The first path is the 2-dimensional Max Pooling. In the second path, the feature map, on the other hand is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling. After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.

>>>>

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-2566-5637} % Add \orcidC{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Viet Dung Nguyen $^{1,\dagger}$\orcidA{}, Ngoc Dung Bui $^{2,\dagger}$\orcidB{} and Khoi Do Hoang $^{3,\dagger}$\orcidC{}}

@@

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Dung Viet Nguyen, Ngoc Dung Bui and Khoi Do Hoang}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Nguyen, D.; Bui, D.; Khoi, D.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

@@

\address{
$^{1}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam \\
$^{2}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam\\
$^{3}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam}

% Contact information of the corresponding author
\corres{Correspondence: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22 (D.N.)}

% Current address and/or shared authorship
\firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Viet Nam} 
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

\section{Introduction} 
\subsection{Problem Statement}
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500 \cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6 \cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase \cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States \cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor \cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.

Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to build solutions to a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions to the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging \cite{11872}.

In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet \cite{04861}, Inception \cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet \cite{03385} \cite{05027}, and NasNet \cite{07012}. Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.

\subsection{Related Works}
Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in \cite{03358}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \cite{06993}, InceptionResNetV2 \cite{00567}, ResNet50 \cite{03385} \cite{05027}, VGG16 \cite{1556} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.

@@

Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3 \cite{00567} model. In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set. Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.

Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet \cite{11946} and SeNET \cite{01507} instead and CutOut \cite{04552v2} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process.

@@

Another state of the art is GradCam and Kernel SHAP \cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research they use three data sets containing HAM10000, BCN-20000 and MSK. Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass.

On the other hand, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021 \cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn.

SkinLinkNet \cite{12602} and WonderM \cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.

@@

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by  \cite{03798} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \cite{10348} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al.

\begin{table}
	\centering
	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
		\hline
		Research & Deep Learning & Machine Learning & Data 
		Augmentation & Feture Extraction & Data set\\
		\hline
		\cite{03358} & x & & x & & HAM10000\\
		\hline
		\cite{03798} & x & x & x & x & HAM10000\\
		\hline
		\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
		\hline
		\cite{09418} & x & & x & & HAM10000\\
		\hline
		\cite{01284} & x & & x & & HAM10000\\
		\hline
		\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
		\hline
		\cite{03225} & x & & x & & HAM10000\\
		\hline
		\cite{12602} & x & & x & & HAM10000\\
		\hline
		\cite{03426} & x & & x & & HAM10000\\
		\hline
		\cite{03910} & x & & x & & HAM10000\\
		\hline
		\cite{05045} & & x & x & x & HAM10000\\
		\hline
	\end{tabular}
	\caption{Related Works Summary. This table is a summary of the approach to skin lesion classification and segmentation. The first column illustrate the cite to the paper research. Column 2 shows a brief summary of the method that is stated in the associated paper.}
	\label{table:related-work-summary}
\end{table}
\subsection{Proposed Method}
In this research, a new model is constructed from the combination of:\\
- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
- Using metadata including age, gender, localization as another input of the model\\
- Using Soft-Attention as a feature extractor of the model\\
- A new weight loss function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Materials}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse \cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the table \ref{table:data-distribution} below:

@@

\subsubsection{Metadata}
The HAM10000 data set \cite{10417} also contain the metadata of patient including gender, age, and the capturing position illustrated in table \ref{table:metadata sample}
\begin{table}[H]
	\centering
	\begin{tabular}{|c c c c |} 
		\hline
		ID & Age & Gender & Local\\ 
		\hline
		ISIC-00001 & 15 & Male & back\\
		\hline
		ISIC-00002 & 85 & Female & elbow\\
		\hline
	\end{tabular}
	\caption{Metadata example in the data set}
	\label{table:metadata sample}
\end{table}
\subsection{Methodology}
\subsubsection{Overall Architecture}
The whole architecture of the model is represented in the figure \ref{fig:main-model}. The model takes two input including Image data and Metadata. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{Definitions/MainModel - Model Form}
	\caption{Overall Model Architecture}
	\label{fig:main-model}
\end{figure}

The figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research. In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module. Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module. InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module. Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/Model Structure}
	\caption{Overall Original Model Architecture. This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge. The detail structure and information can be found at the Apendix \ref{appendix-table:detailed structure model}}
	\label{fig:model-structure}
\end{figure}

The figure \ref{fig:mobile-model-structure}, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module. The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell. 
\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
	\caption{Overall Mobile-based Model Architecture. This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detail structure and information can be found at the Apendix \ref{appendix-table:detailed mobile model structure}}
	\label{fig:mobile-model-structure}
\end{figure}

\subsubsection{Input Schema}
In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form. Before feeding into the backbone model, the images is pre-processed by the input requirement of each model. DenseNet201 \cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152 \cite{03385} \cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet \cite{04861} \cite{04381} \cite{02244}, NasNetMobile and NasNetLarge \cite{07012} require the input pixel is in range of $-1$ and $1$.

On the other hand, the metadata is also used as another input. In the research \cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU \cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

In this paper, the unknowns is kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section. The Input schema is described in the table \ref{fig:input-schema}

@@

\subsubsection{Backbone Model}
In this paper, the backbone models used in this paper are DenseNet201 \cite{06993}, Inception \cite{00567}, MobileNets \cite{04861} \cite{04381} \cite{02244}, ResNet \cite{03385} \cite{05027}, and NasNet \cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.

\begin{table}[H]
	\centering
	\begin{tabular}{|l | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
	\caption{Size and Parameters and Depth of backbone model used in this paper. This table summarizes the properties of the backbone models. The size column illustrates how many space need to store the model in megabyte. The parameters column demonstrate the number of parameters in the associated model. The last column, depth show the number of hidden layers in that model. Parameters and Depth are two crucial element to evaluate the optimized model stated in the Objective section.}
	\label{table:model-summary}
\end{table}

\subsubsection{Soft-Attention Module}
Applying the Soft-Attention layer in deep learning is not a new approach. Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describes the flow of the Soft-Attention module:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the soft-max function to generate K (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

@@

In this paper, the Soft-Attention layer is applied in the same way in this paper \cite{03358}. The Soft-Attention module is described in the following diagram:

@@

After feeding into ReLU function layer, the heat feature map is processed in two paths. The first path is the 2-dimensional Max Pooling. In the second path, the feature map, on the other hand is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling. After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.
